\chapter{The Merton Winter Ball}
\section{General Regulations}
\appnpara There shall be a Joint Standing Committee of the MCR and JCR to be called The Ball Committee, the posts for which are to be open to both common rooms for general election.  The Standing Orders governing the operation of the Ball Committee shall be the same as those set out for all Standing Committees (S.O. 3.4) unless expressly stated otherwise below.

\appnpara There shall be a Merton College Winter Ball in Michaelmas Term once in every three years.  Thus, there shall be a ball in the Michaelmas Terms of 2022, 2025, 2028 and thereafter.

\appnpara The Ball Committee shall exist to provide a self-financing and enjoyable Ball for the College.  

\appnpara The Ball Committee should act always in accordance with the spirit in which the Ball is intended and not seek to profit unfairly from their position.

\section{Election and appointment of the Committee members}

\subsection{The Executive}
 
\appnpara The Committee shall consist of the Ball Chair, Ball Secretary and Ball Treasurer, all of whom are to be elected by secret ballot (see 8 below). These three (hereafter “the Ball Executive”) shall be elected at least one year prior to the date on which the proposed Ball is to be held, and not less than 2 weeks before the end of the term in which the election occurs.  (i.e. if a Ball is to be held in Michaelmas 2022, the Ball Executive shall be elected by the end of 6th Week of Michaelmas 2021). 

\appnpara The outgoing Ball Executive members will each write a short job description that will be circulated to all Junior Members of the College by the Returning Office of the JCR when advertising for candidates.

\appnpara Candidates for the roles of Ball Chair, Ball Treasurer and Ball Secretary must receive written from their Tutors before being allowed to hust for any of the positions, and may not be on the JCR or MCR Executive Committee during their appointment.

\appnpara The process for electing the Ball Executive shall be as for members of the JCR Executive Committee (S.O. 4), except that before the hustings held by the Returning Officer, each of the candidates will be interviewed (in public) by a panel consisting of (at their convenience) the JCR and MCR Presidents and Treasurers, available members of the previous Ball Committee, and any other junior member of the College appointed by the JCR and MCR Presidents.  This panel shall consist of no more than 10 members.  Before this interview takes place, the JCR and MCR Presidents shall consult the Senior Treasurer of the Ball (hereafter ‘The Senior Treasurer’) and the Domestic Bursar about issues arising from previous balls.  

\subsection{Other Committee members}

\appnpara The other members of the Ball Committee, who shall be the Directors of Marketing, Food \& Drinks, Entertainment, Production and Health \& Safety and Security (hereafter, ``Section Directors'' or ``Directors'') shall be appointed by vote of the Ball Executive in consultation with the Senior Treasurer, Domestic Bursar, and MCR and JCR Presidents.  Applications from members of either the MCR or JCR to join the Ball Committee are to be treated equally.  The Ball Executive shall select the best-suited applicant for each committee position, and subject to that shall aspire, if applications allow, to have equal representation of both common rooms in the Ball Committee.

\appnpara Following their appointments, the Section Directors, in conjunction with the Executive Committee, will appoint the members of their teams in the positions outlined below. 

\appnpara ``Committee members'' are henceforth defined as all Executive Committee members, all Section Directors, and all appointed members of their teams.

\appnpara The Structure of the teams shall be appointed according to need with a suggested structure being as follows:
\begin{itemize}
    \item Health, Safety and Security Team: 
    \begin{itemize}
        \item Health and Safety
    \end{itemize}
    \item The Marketing Team:
    \begin{itemize}
        \item Design
        \item Ticketing and IT
        \item Sponsorship
    \end{itemize}
    \item The Food \& Drinks Team:
    \begin{itemize}
        \item Food
        \item Drink and Bars
    \end{itemize}
    \item The Entertainment Team:
    \begin{itemize}
        \item Music
        \item Non-musical Entertainment
    \end{itemize}
    \item The Production Team:
    \begin{itemize}
        \item Marquees, lighting, stages, sound-systems (Production)
        \item Facilities and Timetabling
        \item Decorations
    \end{itemize}
\end{itemize}

\appnpara The JCR and MCR Presidents and Treasurers shall be invited to the bi-weekly meetings held between the Ball Executive and the Senior Treasurer and Domestic Bursar. They may also call for a meeting with the Ball Committee as necessary.

\appnpara The Senior Treasurer, JCR President, and MCR President shall be invited to attend meetings of the Ball Committee and other College Officers may be invited at the Ball Executive’s discretion. Copies of the minutes shall be sent by the Ball Secretary (by default) to: the Senior Treasurer, the Domestic Bursar, and the JCR and MCR Presidents.  

\section{Procedure and chains of command}

\appnpara The Directors of Marketing, Food \& Drinks, Entertainment, and Production (hereafter “The Directors”) shall have direct responsibility for those respective teams. 

\appnpara The Ball Executive shall receive a spoken report from each Director on at least a weekly basis at the committee meeting or a written report in lieu.

\appnpara All expenditures of over £100 must be authorised by the full Ball Committee and recorded in the minutes by the Ball Secretary.

\section{Responsibilities of the Ball Executive}

\appnpara It is the responsibility of the Ball Chair to account for business transacted by the Ball Committee at the General Meetings of the JCR and MCR, or in their absence, another member of the Ball Executive.

\appnpara The Ball Treasurer will prepare accounts each week in the term of the Ball to present to the Senior Treasurer, and for the Ball Chair to present to the JCR and MCR General Meetings.

\appnpara The Ball Secretary shall record business transacted at meetings of the Ball Committee. By the passing of a motion at an Ordinary General Meeting, either the JCR or the MCR may request access to these minutes.

\appnpara It is the responsibility of the Ball Chair to seek formal permission to hold a Ball from the Governing Body through the Principal of Postmasters and to seek approval for all subsequent arrangements when and if such permission is granted, unless the Ball Chair is elected later than in the timetable set out in 5 above, in which case the JCR and MCR Presidents shall make the application for permission in general terms.

\appnpara The outgoing Ball Chair shall deposit copies of all Ball Files with the College Archivist.  The Ball Committee may consult this archive to help them with their duties.

\appnpara The outgoing Ball Executive shall compile reports (including accounts) and submit them to the JCR, MCR, Senior Treasurer, and Domestic Bursar, as well as depositing copies in the College Archive.  

\section{Responsibilities of the Directors}

\appnpara The Directors shall manage their teams, holding meetings at least once a week during the term of the Ball and the term before.

\appnpara All Directors shall work with the Ball Treasurer to set budgets for their team members, and shall be jointly responsible (with the Ball Treasurer) for making sure that team members adhere to their budgets. 

\section{Responsibilities of all Committee members}

\appnpara All outgoing members of the Committee shall produce reports to be deposited in the College Archive by the Ball Chair.  

\appnpara All members of the Committee shall be prepared to work soberly on the night of the Ball itself, and at any marketing or similar events related to the Ball, as requested by the Ball Chair or their team Director.

\section{Dismissal of Committee members and members of the Director's teams}

\appnpara Unlike the Chair of a JCR Standing Committee, the Ball Chair may, with the agreement of both the Ball Treasurer and Ball Secretary, and in consultation with the JCR and MCR Presidents and the Senior Treasurer, dismiss a Section Director (not including the Ball Treasurer or Secretary).  

\appnpara Likewise, the Ball Chair may dismiss an appointed member of a Section Director's team with the agreement of both the Ball Treasurer and Ball Secretary, and in consultation with the member’s Director, the JCR and MCR Presidents and the Senior Treasurer.

\appnpara The Ball Chair may suspend the Ball Treasurer and/or Ball Secretary, but only with the explicit agreement of the Senior Treasurer and the JCR and MCR Presidents.  

\appnpara The Ball Chair, Ball Secretary and Ball Treasurer may only be dismissed by the passage of a motion of no-confidence passed in General Meetings of both the JCR and MCR, along with the agreement of the Senior Treasurer.  

\appnpara In the case of the dismissal of a member of the Ball Executive, and immediately thereupon, the Returning Officer shall declare nominations open for a replacement.  The process shall be as set out in 2.1. above, excepting that the timetable may be hastened at the discretion of the Returning Officer.  In any case, the nominations must be open for at least 48 hours.  A dismissed member of the Ball Executive or Ball Committee shall be eligible to stand in the election.  

\section{Finance}

\appnpara The Ball Treasurer shall produce a provisional budget to be published for and presented to Ordinary General Meetings of the JCR and MCR six months before the Ball.

\appnpara The provisional budget shall provide for a 10\% safety net in expected expenditure.  If over 90\% of expected income is realise then, at the discretion of the JCR and MCR Executive Committees, alongside the Senior Treasurer, one half of the Safety Net may be spent by the Ball Committee on the Ball.  There must, therefore, at all times be a safety net of at least 5\%.

\appnpara If money has been placed in the``roll-over fund'' (see 8.8 below) as a result of the previous Ball, this money shall be counted as income in the provisional budget.

\appnpara A financial report on the Ball shall be presented to every Ordinary General Meeting in the term of the Ball and the term beforehand to the JCR and MCR.

\appnpara By default, the JCR and MCR shall underwrite the Ball; no money shall be paid out of JCR or MCR accounts for the Ball before the General Meetings have been informed.

\appnpara It is suggested that an initial loan be made by both the JCR and MCR (through motions in their Ordinary General Meetings) to cover early costs.  The Ball Committee shall borrow an equal sum from both common rooms.

\appnpara In the event of any loss made by the Ball, all benefits to the Ball Committee, including the selling of Ball swaps and assets of the Ball, shall be realised before any loss is incurred by the JCR and MCR.  Any loss incurred shall be split equally by the JCR and MCR.  

\appnpara In the event of any profit being made by the Ball, all surplus funds and remaining assets shall be for the use of the next Ball Committee.   Accounts of such funds and assets shall be included in the Ball Treasurer's report.  
