\chapter{The Charities Sponsorship Fund and Junior Members Charities Committee}
\appnpara The purpose of the Charities Sponsorship Fund (henceforth, the ``Sponsorship Fund") is to support Junior Members in the pursuit of charitable causes.
\appnpara The Merton College Junior Members Charities Committee (henceforth ``the Charities Committee") shall have the authority to make donations from the Sponsorship Fund. For advice concerning applications to the Sponsorship Fund, Junior Members are referred to the Charities Representative of their respective Common Room.
\appnpara The Charities Committee shall consist of the President, Treasurer, and Charities Representative of the JCR, and the same of the MCR, and shall meet at least once a term. The Charities Committee shall be co-chaired by the Charities Representatives of the JCR and MCR, and each Common Room shall have three votes. Quorum for a Charities Committee meeting shall be all six members present and voting. There shall be no abstentions from a vote, and an application requires more votes in favour than against to pass. JCR and MCR Representatives on the Charities Committee serve ex officio on said Committee and it shall be permissible for their votes to be directed by their respective Common Room according to its rules.
\appnpara Applications for the Sponsorship Fund should be completed on the form available on the JCR website or from one of the Charities Representatives, and presented to that Charities Representative no later than two days before the Charities Committee meeting. The form shall be completed by the applicant, presented to the Charities Representative, and considered by the Charities Committee. The Charities Committee shall review its application and approval process annually in its meeting in Hilary Term.
\appnpara The maximum amount that can be granted to any one Junior Member in any one application is £200, or in exceptional circumstances £500. Applications must show that other sources of funding are also being sought, and grants from the Sponsorship Fund may not be more than 50\% of the total raised for the activity. The distribution of the Sponsorship Fund rests with the Charities Committee.
\appnpara Extraordinary Meetings of the Charities Committee may be summoned by a simple majority resolution in the General Meeting of either the JCR or the MCR. There shall be two possible reasons for an Extraordinary Meeting: a) to consider an urgent application, the timing of which results from no fault of the applicant or b) to reconsider an application rejected by the immediately preceding Charities Committee meeting. An Extraordinary Meeting shall run along the same lines as detailed in paragraph 3 of this Appendix.
\appnpara Preference shall be given to those Junior Members who have not previously applied to the Sponsorship Fund over those who have, though there is no limit on the number of times a Junior Member may apply for grants from the Sponsorship Fund.
\appnpara The Charities Representatives and the Treasurers shall be responsible for publishing termly accounts of Sponsorship Fund expenditure to their respective Common Rooms.  The Charities Representatives shall request feedback material from successful applications to be posted on Common Room noticeboards to ensure Junior Members are aware of how Sponsorship Fund expenditure has been used.
\appnpara This Appendix may only be altered with the approval of the General Meeting of both the JCR and the MCR.
