\chapter{The Charities Ballot} \label{app:charities_ballot}

\appnpara The purpose of the Junior Members’ Charities Ballot is to facilitate Junior Members donating to worthwhile causes.
\appnpara Unless they choose to opt out, Junior Members shall donate £10 through the Charities Ballot at the end of every term.  This donation shall be charged through battels and appear in arrears.
\appnpara The £10 shall be split equally (so that each cause receives £2 per normal donation) between:
\begin{enumerate}
\item The two permanent Junior Members' charities (Icolyn Smith Foundation and the Wolvercote Young People's Trust)
\item The Junior Members' two nominated charities being supported for the academic year
\item The Charities Sponsorship Fund
\end{enumerate}
\appnpara Any money assigned to the Sponsorship Fund that remains unallocated after the end of Full Term shall be divided equally between the other four charities.
\appnpara The Charities Representatives shall contact all members of their Common Rooms to inform them of their option to opt-out of the termly charities levy with a deadline of Friday of 7th Week, to give sufficient time to inform the bursary. Any opt-outs shall be treated in complete confidence by the Charities Representatives.
\appnpara During 6th Week of Michaelmas Term the Charities Representatives shall run a ballot to decide which two charities the Junior Members wish to support for the academic year. Nominations for the Ballot shall be requested from Sunday of 5th Week. The Charities Representatives shall publish a list of the nominated charities on Sunday of 6th Week. This shall include each charity’s website address (if applicable), a brief summary of their work and any history of nomination by the Junior Members. Each Junior Member can vote for up to two charities. The ballot shall close on Saturday of 6th Week and the result shall be announced at the next General Meeting of each Common Room.
\appnpara This Appendix may only be altered with the approval of the General Meeting of both the JCR and the MCR.
