\chapter{Memoranda}
\section{JCR-MCR BOP Security Cost Sharing}
\textit{Agreed with MCR and approved by both JCR and MCR in HT23}

\appnpara The JCR and MCR commit to sharing the cost of BOP security in line with the formula outlined in this memorandum. 
\appnpara The MCR commits to covering $(25+0.5n)$\% of BOP security costs incurred, where $n$ is the average number of MCR members attending BOPs during one term with the maximum contribution from the MCR capped at 50\%. The remaining costs are to be incurred by the JCR.
\appnpara MCR contributions are to be calculated before start of term - attendance figures from the previous term will be used to calculate the contribution for the upcoming term. The MCR commits to sharing the exact figures used to calculate their final contributions with the JCR.
\appnpara In return, the JCR guarantees that 25\% of all available BOP tickets are to be made available for MCR members as early access tickets. These tickets will be released 24 hours in advance of the general ticket release and any unsold MCR tickets will be returned to the general pool. 
\appnpara If the college makes significant changes to the BOP booking system, this arrangement shall be amended. 

\section {JCR-MCR Games Room Maintenance Fee}
\textit{Agreed with MCR and approved by both JCR and MCR in HT23}
\appnpara In order to enable the JCR to sustainably maintain the state of the Games Room (formally the Mackeith Room), the MCR agrees to pay the JCR a maintenance fee.
\appnpara Commencing in Trinity Term 2023, the MCR commits to paying the JCR a termly maintenance fee of £246. 
\appnpara The arrangement outlined in this memorandum will remain in place for two academic years; the last term for which it will apply is Hilary Term 2025. In light of the experience of managing maintenance from these two years (in particular, the separation between projected and actual maintenance costs), the JCR and MCR should agree upon a new maintenance fee. 
