\chapter{External Affiliations}
\textit{NB: This is an Agreed Standing Order.}
\npara In accordance with Article \ref{Art:Affiliations}, the JCR may decide to affiliate to External Organisations for up to fourteen months by a Motion passed by the General Meeting or by Referendum.  Such a decision must include a decision to introduce a regulatory document, approved as part of the same Motion or Referendum, governing how the JCR shall interact with the organisation, including any details of who should represent the JCR.  Any such regulatory document is given binding force by this Standing Order and may be amended by a Motion passed by the General Meeting or by Referendum.
\npara The Executive Committee must publish notice of any affiliation decision, stating the name of the organisation and details of any subscription or similar fee paid or proposed to be paid and of any donation made or proposed to be made to the organisation.  The Executive Committee shall ensure that such notice is given to the College (by sending it to the Senior Treasurer of the JCR and to the Senior Tutor for transmission to the Warden and Tutors' Committee) and to all Undergraduates.
\npara The Executive Committee shall ensure a motion is submitted to the second Ordinary General Meeting of Michaelmas Term resolving to renew current affiliations. This motion, listing the current affiliations, shall be voted on in parts, with each part requiring a simple majority to pass.
\npara By petition of ten or more Ordinary Members, addressed to the Executive Committee via any Trustee, the question of continued affiliation to any External Organisation shall be decided by Referendum, in accordance with S.O.5.
