\chapter{Finances}
\textit{NB: This is an Agreed Standing Order.}
\section{Records and day-to-day administration}
\npara The Executive Committee shall keep accounting records in respect of the JCR which:
\begin{enumerate}
\item are sufficient to explain all of the JCR's transactions;
\item are such as to disclose, at any time, the financial position of the JCR at that time; and
\item enable true and fair accounts to be prepared and examined from time to time.
\end{enumerate}
\npara The accounting records referred to in S.O. 8.1.1. must in particular contain:
\begin{enumerate}
\item entries showing from day to day all sums of money received and expended by the JCR and the matters in respect of which the receipt and expenditure takes place; and
\item a record of the assets and liabilities of the JCR.
\end{enumerate}
\npara A copy of the annual financial report must be kept by both the Treasurer and the Vice President, and handed over to the incoming Treasurer and Vice President before they begin their term in office, as elected in accordance with the Standing Orders.
\npara The Executive Committee shall monitor all expenditure and the maintenance of assets to ensure that the income and property of the JCR is applied appropriately.
\npara On taking office, the Executive Committee shall audit the financial and accounting records produced by the previous Executive Committee.
\npara The Executive Committee shall open and operate such bank and other accounts as it considers  necessary, in accordance with Article \ref{Art:TrusteePowers} and S.O. 8.4.
\npara In accordance with Article \ref{Art:Finances}, unless the Executive Committee determines otherwise, thus withdrawing or amending the delegation, the Treasurer shall be responsible for the day-to-day administration of the JCR's finances as laid out in S.O. 8.1.  The powers and responsibilities of the Executive Committee in S.O. 8.1. shall be delegated to them, in accordance with S.O. 8.4, save that the Executive Committee remain responsible for the application of income and property, in accordance with Article \ref{Art:Application}.
\section{Budgets and reserves}
\npara For each Financial Year, the Executive Committee shall seek the approval of the College for the JCR's Annual Budget, following consultation with relevant Officers. The Executive Committee shall not authorise or incur expenditure in excess of 105\% of the total planned expenditure in the Annual Budget, except to meet liabilities already incurred or with the express authority of the College or if it is necessary to do so.
\npara The Executive Committee shall budget to maintain a reserve of at least 60\% of the general operational income received for the previous Term.  This is in order to offset the risk of unexpected costs, unplanned overspend or a reduction in income.  In accordance with Article \ref{Art:TrusteePowers}, the Executive Committee may budget to maintain a larger reserve, in accordance with a written reserves policy. 
\npara If the level of reserves is below that determined in accordance with S.O. 8.2.2., the Executive Committee shall budget to restore at least 50\% of the difference over the Financial Year, unless the General Meeting resolves to approve an alternative strategy.  If the level of reserves is significantly above that determined in accordance with S.O. 8.2.2., the Executive Committee shall bring a proposal to the General Meeting to spend at least one-third of the excess on long-term improvements.
\npara The Executive Committee shall ensure that the JCR is suitably insured against potential liabilities.
\section{Accountablility}
\npara The JCR's finances shall be a matter of public record and shall be conducted in a responsible and accountable fashion.  The Executive Committee shall be accountable to the General Meeting for all expenditure and movement of moneys. A presentation providing an overview of the annual finances must be given in the last OGM of the academic year by the Treasurer to the JCR.
\npara The Executive Committee shall ensure that the income and property of the JCR is applied solely towards the promotion of the Objects, in accordance with Article \ref{Art:Application}.
\npara The Executive Committee shall provide the most recent Annual Accounts of the JCR to any person who requests them.  If they request the accounts by a means other than suitable Electronic Means, the Executive Committee may require the payment of such reasonable fee as may be required in respect of the costs of complying with the request. The most recent annual accounts should also be available on the JCR website.
\npara The Executive Committee shall ensure that termly Budgets and Accounts are submitted promptly to the JCR and to the College. The Budget for the upcoming Term and the Accounts for the previous Term shall be presented to the first OGM of each Term.  The Annual Budget shall be presented to the first OGM after its approval.
\npara Termly or more frequently, the Executive Committee shall designate one or more suitably independent Trustees who shall internally audit the financial and accounting records of the JCR produced for that period.
\npara For each financial year, the Executive Committee must obtain the approval of the College for the JCR's budget. 
\npara For each Financial Year, the Executive Committee shall approve and submit Annual Accounts to the College, after all relevant records have been internally audited in accordance with S.O. 8.1.3. and S.O. 8.3.5.  The Annual Accounts and a report on the activities of the JCR over the Financial Year and the main aims for the coming year shall be submitted to an OGM in Michaelmas Term.
\begin{enumerate}
    \item This annual financial report must include a balance sheet, and report the monies held in all accounts in the name of the JCR, to include the JCR Charities account and the JCR account.
\end{enumerate}
\npara Unless an audit is required, for each Financial Year the Annual Accounts of the JCR shall be independently examined by an independent person who is reasonably believed by the Executive Committee to have the requisite ability and practical experience to carry out a competent examination of the accounts, in accordance with sections 144-161 of the Charities Act 2011.
\npara All subscriptions paid to Affiliated Organisations shall be listed in the relevant termly Accounts, in accordance with S.O. 9.  Similarly, for each Financial Year, the list of all Affiliated Organisations and subscriptions paid shall be included in the Annual Accounts.
\npara The College has the right to inspect all of the financial and accounting records of the JCR on request. The Executive Committee is responsible for addressing such requests.
\npara The Base Income is the capitation from the College received for that Term, unless the General Meeting determines otherwise.
\section{Delegation and financial controls}
\npara In accordance with Article \ref{Art:Finances}, the Executive Committee may only delegate control of the JCR's finances or permit expenditure to be incurred on behalf of the JCR in accordance with the requirements of S.O. 8.4.  Subject to this Standing Order, the Executive Committee may delegate such control or permit such expenditure in all ways allowed by the Constitution.
\npara Where direct control of JCR funds is delegated, at least two Trustees must have access to the account in which it is kept and the approval of at least one Trustee must be given for any transfer out of the account.
\npara Expenditure may only be made against an invoice presented to the JCR and expenditure made on the JCR's behalf may only be reimbursed against a receipt presented to the JCR, except in accordance with S.O. 8.4.8.  The Executive Committee must retain copies of all such invoices and receipts.
\npara A Trustee authorised by the Executive Committee may make expenditure, in accordance with a budget approved by the Executive Committee, or reimburse for such expenditure made on the JCR's behalf, up to a limit of 2\% of the Term's Base Income for each distinct purchase or expense.  Purchases listed on the same invoice are not distinct, neither are expenses listed on the same receipt.  The Treasurer should usually be authorised in this fashion.
\npara Subject to S.O. 8.4.4., all other expenditure and reimbursement requires the approval of the Executive Committee or, where control of funds is delegated to a Sub-Committee, the Sub-Committee.
\npara The Executive Committee (and its Sub-Committees) shall not intentionally authorise or incur expenditure (except to meet liabilities already incurred or if it is necessary to do so) in any of the following ways without the express authority of the General Meeting.
\begin{enumerate}
\item On any single item not listed in the most recent termly Budget in excess of 5\% of the most recent Term's Base Income.
\item On any item listed in the Budget in excess of 115\% of the planned expenditure for that item.
\item In excess of 110\% of the total planned expenditure of the most recent termly Budget.
\end{enumerate}
\npara The Executive Committee shall not budget more than 5\% of the most recent Term's Base Income on expenses of the Executive Committee (and its Sub-Committees).
\subsection{Authorising expenditure without receipts or invoices}
\npara Subject to the Constitution and Standing Orders, the Executive Committee (or, where relevant, a Sub-Committee) shall have the following powers.
\npara The Executive Committee (or a Sub-Committee so authorised) may authorise donations to be made by way of subscription to an Affiliated Organisation in accordance with S.O. 9. or to a charitable cause to further the Objects, provided that the Committee is reasonably satisfied that the organisation in receipt of the donation is properly run and will apply the funds appropriately.
\npara The Executive Committee (or a Sub-Committee so authorised) may make grants to Undergraduates or to support Undergraduates on the basis of a costed plan for the use of the funds in furtherance of the Objects and appropriate assurances and checks that the funds will be thus applied.
\npara The Executive Committee may invest funds and delegate the management of funds in the same manner and subject to the same conditions as the trustees of a trust are permitted to do by the Trustee Act 2000. 


