\chapter{General}
\textit{NB: This is an Agreed Standing Order}
\section{Interpretation and records}
\npara The definitions given in Appendix \ref{App:Defs} shall apply for the interpretation of all Standing Orders.
For the purposes of interpretation, footnotes do not form part of the Standing Orders.
\npara The Executive Committee shall be responsible for maintaining an up-to-date master copy of the Constitution and Standing Orders, which shall be published on the JCR Website.
The content shall only be amended in accordance with the Constitution.
\npara For the purposes of the Constitution, consequential renumbering and updating of references shall not be amendment and may be performed at the discretion of the Executive Committee.
\npara Appendices shall have force only to the extent that they are given force by one or more references to each Appendix in the Standing Orders.  Amendment of an Appendix shall be considered as an amendment of the applicable reference or references in the Standing Orders.
\section{Membership} \label{SO:Membership}
\npara \label{SO:OptOut} In accordance with Article \ref{Art:Members} of the Constitution and this Standing Order, a person who is eligible to be an Ordinary Member or Honorary Member has the right to not be a Member.
\npara No later than Sunday of the second Week of Michaelmas Term each year, the Vice President shall give notice to Members of the right provided in S.O. \ref{SO:OptOut}.
\npara A person may exercise the right referred to in S.O. \ref{SO:OptOut} at any time, by indicating in writing, addressed to the Vice President, that the person does not wish to be a Member.
\npara A person who previously exercised the right provided in S.O. \ref{SO:OptOut} may revoke the exercise of that right and become a Member at any time, by indicating in writing, addressed to the Vice President, that the person revokes the person's previous indication and now wishes to be a Member.
\npara In accordance with the Constitution, a person who has exercised the right provided in S.O. \ref{SO:OptOut} retains the right of appropriate access to the services and facilities provided by the JCR.
Such a person is entitled to use all Common Room facilities and to participate in the JCR's social, cultural, artistic, welfare, charitable and sporting activities, subject to reasonable restrictions, but is not entitled to enjoy the other rights and privileges enjoyed by Members under the Constitution.
\npara The Vice President shall maintain a register of Members, including an email address at which the Member can be contacted.
\npara The Executive Committee is responsible for ensuring that the Vice President fulfils the duties given in S.O. \ref{SO:Membership} and may reallocate them if necessary.
Such a reallocation must be clearly communicated to the Members, including through the General Meeting.
\section{Data Protection}
\npara The Executive Committee shall maintain an information asset register, of all personal data held by, or on behalf of, the JCR.  The Executive Committee shall identify and document the lawful basis on which personal data is processed.
\npara The Executive Committee shall establish and monitor appropriate procedures to protect the security of the all personal data held and processed by the JCR, or on the JCR's behalf.
\npara The Executive Committee shall establish and publicise appropriate procedures to allow individuals to access any personal data of theirs which the JCR controls and to exercise any other rights that they may have in relation to personal data.