\chapter{Role Descriptions}
\textit{NB: This is an Internal Standing Order}
\section{The Executive Committee}
\npara The Executive Committee shall be composed of the following members.
\begin{enumerate}
	\item President
	\item Vice President
	\item Treasurer
	\item Access and Equal Opportunities Representative
	\item Academic Affairs Representative
	\item Two Welfare Officers
	\item Two Entertainment Representatives
\end{enumerate}
\npara The two Entertainment Representatives and Welfare Officers shall be elected by Joint Election, except that a By-Election for a single Entertainment Representative or Welfare Officer shall be by Individual Election. For the avoidance of doubt, all other members of the Executive Committee shall be elected by Individual Election. 
\section{The JCR Committee}
\npara The JCR Committee shall be composed of the following members.
\begin{enumerate}
	\item Members of the Executive Committee
	\item Affiliated Organisations and Careers Representative
	\item Arts Representative
	\item Charities Representative
	\item Disabled Students' Representative
	\item Environment Representative
	\item Ethnic Minority Students' Representative (BME Representative)
	\item Food and Bar Representative
	\item Gender Equality Representative
	\item International Students' Representative
	\item LGBTQIA+ Representative
	\item Transgender Representative
	\item Publications and Social Media Officer (Walter de Merton)
	\item Sports and Recreation Representative (Admiral of the Fleet)
	\item Suspended Students' Representative
	\item Social Backgrounds Representative
	\item Information Technology Officer
\end{enumerate}
\npara The Secretary to the JCR Committee shall be the Vice President.
\section{Non-Committee Officers}
\npara The JCR shall have the following non-Committee Officers.
\begin{enumerate}
	\item Returning Officer
	\item Events Photographer
	\item Subject Presidents
\end{enumerate}
\section{President}
\npara The President shall be responsible for the general operation of the JCR and working to coordinate its internal and external affairs. 
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the President shall include those listed below.
\begin{enumerate}
	\item Upholding the Constitution and Standing Orders and raising with the Executive Committee any disputes in relation to their interpretation.
	\item Supervising the JCR's affairs, including compiling the JCR term card in conjunction with the Vice President.     
	\item Supervising the Executive Committee Officers in the conduct of their day-to-day duties.
	\item Acting as the Chair of the General Meeting, in accordance with S.O. 6.7.     
	\item Convening and chairing meetings of the Executive Committee at least eight times a term, and compiling the agenda for these meetings, in accordance with S.O. 2.2. and Article \ref{Art:TrusteeDecisions}.
	\item Communicating JCR policy to the College, including attending the meetings of the following: Governing Body, Joint Committee, Domestic Committee, Warden and Tutors' Committee, and Development Committee.
	\item Advancing the interests of the JCR or of any of its Ordinary Members (on request) to the relevant College Authorities.
	Communicating the College's policies to the JCR.     
	\item Advancing the interests of the JCR externally to the Presidents' Committee and, in association with the Affiliated Organisations and Careers Representative, any organisation to which the JCR chooses to affiliate itself under S.O. 9.
	\item Cultivating favourable relations between Junior and Senior Members of the College.
	\item Acting as spokesperson and representative for the JCR and JCR Committee.
	\item Coordinating the upkeep and improvement of the MacKeith Room, TS Eliot Room, JCR Room and JCR Store Room.
	\item Organising and coordinating Freshers' Week in association with the Executive Committee, including organising the circulation of the Freshers' Guide and International Students' Guide; producing a written report on Freshers' Week including recommendations for improvement.
	\item Organising and coordinating the Time Ceremony in association with the Executive Committee; producing a written report on the Time Ceremony, including recommendations for improvement.
	\item Regularly communicating progress on JCR issues to the JCR via email, at least once a week during Full Term.
	\item Maintaining and updating subscriptions to the JCR's mailing list.
	\item Maintaining and updating an archive of the JCR's affairs for the year, and updating the `knowledge bank'.
	\item Negotiating with the College Authorities over Battels levels in conjunction with the Treasurer, and informing the General Meeting about the progress of such negotiations.
	\item Attending the meetings of the Junior Members' Charities Committee (Appendix D).
	\item Attending or appointing a JCR representative for the Garden Committee.
	\item Acting as the Designated Officer for the Affiliated Organisations and Careers Representative.
\end{enumerate}
\section{Vice President}
\npara The Vice President shall be responsible for supporting the President in the coordination of JCR activities and maintaining JCR records, except financial records.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Vice President shall include those listed below.
\begin{enumerate}
    \item Assisting or representing the President as required.
    \item Acting as Secretary to the General Meeting subject to S.O. 6.8. and Article \ref{Art:Minutes} on behalf of the Executive Committee.
    \item Retaining a digital file of all General Meeting Agendas and Minutes for future reference, on behalf of the Executive Committee.
    \item Acting as Secretary to the Executive Committee subject to S.O. 2.2.
    \item Acting as Secretary to the JCR Committee subject to S.O. 2.3.
    \item Liaising with College over accommodation, including conducting the Room Ballot according to the procedure set out in Appendix C and maintaining the room database which is to be updated annually.
    \item Organising the JCR photo early in Trinity Term.
    \item Publicising relevant and interesting events and information to the JCR via appropriate means, and maintaining the JCR noticeboard.
    \item Arranging the publication of a yearbook, leavers' hoodies, and related items, to be distributed to leavers before the end of Trinity Term.
    \item In conjunction with the President, ensuring that all relevant JCR documentation is retained for the benefit of future Executive Committees and other JCR Committee members, and encouraging all sports captains and College society presidents to do the same. Copies of significant JCR documents should also be passed to the College Archivist, in accordance with relevant JCR policy. 
    \item After appropriate consultation with Members on their preferences, purchasing video games or further controllers compatible with the JCR’s Nintendo Switch, to a maximum cost of £100 per term and placing those games in the JCR TV Room.
    \item Compiling and circulating the JCR term card before 1st Week of each term, in conjunction with the President. 
    \item Seeking approval for the draft JCR term card in 0th week from the Deputy Principal of Postmasters and any other relevant college authorities. 
    \item Acting as the Designated Officer for the Publications and Social Media Officer, the Environment Representative, and the Information Technology Officer.
\end{enumerate}

\section{Treasurer}
\npara The Treasurer shall be responsible for the day-to-day management of the JCR's finances, by and with the consent of the Executive Committee in accordance with Article \ref{Art:Finances} of the Constitution and S.O. 8., and advising the JCR on financial matters.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Treasurer shall include those listed below.
\begin{enumerate}
	\item Managing the JCR finances responsibly.     
	\item Negotiating with the College Authorities over Battels levels in conjunction with the President, and informing the General Meeting about the progress of such negotiations.
	\item Advising the JCR Committee and Executive Committee on financial matters.
	\item Attending the meetings of the Junior Members Charities Committee (Appendix D).          
	\item Attending the meetings of the Ball Committee if existent.     
	Ensuring maintenance of electrical equipment for which the JCR is responsible.     
	\item At the start of an academic year, the incumbent Treasurer shall be responsible for auditing the annual accounts of the previous Treasurer and of any other budgets devolved to members of the JCR Committee.
	The incumbent Treasurer shall report their findings to the JCR at the first OGM of the subsequent term.
	A copy of the audited accounts shall be kept in the JCR Store Room as well as archived digitally to be handed over to the successor.
	\item Acting as the Designated Officer for the Charities Representative and the Sports and Recreation Representative.
\end{enumerate}
\section{Access and Equal Opportunities Representative}
\npara The Access and Equal Opportunities Representative shall be responsible for promoting and advancing equality within the JCR, College and University and working to coordinate all access-related activities. 
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Access and Equal Opportunities Representative shall include those listed below.
\begin{enumerate}
	\item Encouraging applications to the College and to the University, and encouraging a greater awareness of access-related issues among all members of the College.     
	\item Working proactively to advance equality for all members of the College, within the College in general and the JCR specifically, and acting to prevent discrimination or prejudice of any kind, in accordance with Article \ref{Art:Equality} of the Constitution. 
	\item Organising open days, offer holder days, and related events such as summer schools in liaison with the relevant college authorities, committee members, and interested Ordinary Members.
	\item Liaising with the relevant College officer to organise and support access initiatives in the College, including coordinating the Student Ambassadors for schools visits and access events.
	\item Representing the JCR on external committees convened by Affiliated Organisations for the consideration and advancement of Target Schools or admissions-related issues.
	\item Coordinating the representation of the JCR to the College on matters of equality, including liaising with individuals in the JCR and the College, as appropriate.
	\item Convening and chairing the Equality Sub-Committee at least once a term (S.O.~\ref{ssec:equality-committee}).
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee})     
	\item Forwarding information on access-related events and issues to the JCR on a regular basis via email. 
	\item Advancing matters of equality that do not fall under the remit of other members of the Equality Sub-Committee including, but not limited to, religious issues. 
	\item Providing a confidential listening service to Undergraduates.
	\item Acting as the Designated Officer for the Disabled Students’ Representative, the Ethnic Minority Students’ Representative, the Gender Equality Representative, the International Students’ Representative, the LGBTQIA+ Representative, the Transgender Representative and the Social Backgrounds Representative.
	\item Sharing information on access-related events, news, and general outreach media on the public, student-run, JCR access Instagram page. 
	\item Using the JCR access Instagram page to communicate with current and prospective students in an appropriate manner on access and equality-related subjects. 
	\item Recruiting student ambassadors at the Merton college Freshers' fair in 0th Week of Michaelmas Term.
	
\end{enumerate}
\section{Academic Affairs Representative}
\npara The Academic Affairs Representative shall be responsible for advancing all aspects of academic-related liaison and cooperation between the JCR and College and acting to address all relevant academic issues for Undergraduates.  
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Academic Affairs Representative shall include those listed below.
\begin{enumerate}
	\item Improving academic relations, practices and regulations within both the College and the University.     
	\item Liaising with the library staff concerning issues pertaining to Undergraduates.
	\item Attending meetings of the Library Committee and reporting back to the JCR.
	\item Representing the JCR on external committees convened by Affiliated Organisations for the consideration and advancement of academic affairs or related issues and reporting back to the JCR.     
	\item Acting as a contact point between members of the JCR and the College on the subject of academic feedback, including the running of the JCR Academic Forum.
	\item Promoting and supporting initiatives organised by the College aimed at giving additional academic support to students.     
	\item Encouraging use of the parenting scheme and graduate mentoring scheme as sources of academic advice.     
	\item Attending meetings of the Welfare Sub-Committee.     
	\item Co-ordinating and providing support to the Subject Presidents.     
	\item Co-ordinating the subject teas in Freshers' Week in conjunction with the Subject Presidents in conversation with the timings of tutor meetings and library tours.
	\item Liaising with the College over academic-related activities in Freshers' Week, including the library inductions.
	\item Liaising with the Academic Office over the organisation of the Freshers' Study Skills Sessions, the Exam Forum for First-Years and the Finalists' Forum with the subject presidents and Senior Tutor.
	\item Acting as a contact point for students whose collections have not been returned by the end of 4th Week and liaising with the Academic Office to update students on the status of their collections.
	\item Updating the lists of Subject Presidents and society presidents and informing the Academic Office of when the holders of these positions change.
	\item Acting as the Designated Officer for the Subject Presidents.
	\item Overseeing the conducting of Subject President elections in accordance with SOs \ref{ssec:roles_subjpres_electionduty}, \ref{ssec:roles_subjpres_electionreq}, \ref{ssec:roles_subjpres_replace} and \ref{ssec:roles_subjpres_electionmisc}.
	\item Undertaking any such obligations as imposed by the operation of the `Merton Initiative for the Funding of Subject Societies' (`MIFSS') in accordance with SOs \ref{ssec:roles_subjpres_funding} and \ref{ssec:roles_subjpres_fundingguidance}.
	\item Passing on information related to careers and postgraduate opportunities to the JCR.
\end{enumerate}
\section{Welfare Officers}
\npara The Welfare Officers shall work together to support the welfare needs of Undergraduates.
\npara \label{resp:welfare-officers} In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Welfare Officers shall include those listed below.
\begin{enumerate}
	\item Attending the Peer Support training sessions and providing a confidential listening service to members of the JCR, by weekly drop-in sessions during Full Term or any other method by which the service can be adequately provided.
	\item Providing information about professional welfare services available from the University or elsewhere in Oxford.     
	\item The collation and provision of information on College and University hardship funds.     
	\item The promotion of the welfare and safety of Undergraduates.     
	\item Liaison with appropriate welfare-related authorities in and out of College.     
	\item Convening and chairing meetings of the Welfare Sub-Committee at least once a term (S.O.~\ref{ssec:welfare-committee}).     
	\item Advising the JCR, JCR Committee and Executive Committee on welfare issues.     
	\item The provision of the weekly JCR tea.     
	\item Organising the JCR parenting scheme.
	\item Managing the purchase and provision of sexual health related items and female sanitary products for the JCR.
	\item Attending Affiliated Organisations' welfare representative forums, and relevant welfare seminars.
	\item Arranging and running welfare events throughout the year in addition to events organised by the Entertainment Representatives.
	\item Acting as the Designated Officers for the Suspended Students’ Representative and the two Welfare Helpers.
	\item \label{SC:peer-choice} Choosing the members of the JCR Committee to be Peer Support trained, in liaison with the JCR Committee, with consideration to which members of the JCR Committee are likely to find Peer Support training most helpful and the overall composition of those being Peer Support trained, including consideration of gender, sexuality, ethnic background, social background,  home/international status, faith, disability, and visibility in College life.
	\item Arranging appropriate welfare provisions at BOPs conducted by the Entertainment Representatives. This includes, but is not limited to, sober supervision and the recruitment of others for such purposes (`BOP Angels'), ensuring access to non-alcoholic beverages at BOPs, provision of quiet and rest spaces, and providing food.
\end{enumerate}
\section{Entertainment Representatives}
\npara The Entertainment Representatives shall work together to support and organise social, cultural and recreational activities and events for Members  and their guests.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Entertainment Representatives shall include those listed below.
\begin{enumerate}
	\item The conception, planning, organisation, publicising and execution of events for the entertainment of all members of the JCR.
	\item Informally designating, if appropriate, certain willing Ordinary Members to assist with the operation of events.
	\item Circulating an electronic term card to the JCR via email and social media before the beginning of each relevant term.
	\item The organisation of social events during Freshers' Week in liaison with the Executive Committee.
	\item Any required liaison with the College Authorities before, during or after events, including seeking permission in advance from the Deputy Principal of Postmasters for any such events to take place, and seeking approval for the draft JCR term card in 0th week, in liaison with the President and Vice President where appropriate.
	\item Controlling entertainment finances in liaison with the Treasurer.
	\item Acting as the Designated Officers for the Arts Representative, the Food and Bar Representative and the Events Photographer.
\end{enumerate}
\section{Affiliated Organisations and Careers Representative}
\npara The Affiliated Organisations and Careers Representative shall manage the JCR's relationship with any Affiliated Organisations, attending meetings and representing the views of the JCR as appropriate.
\npara In each Academic Year, the Scheduled Election of the Affiliated Organisations and Careers Representative shall take place in the third OGM of Michaelmas.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Affiliated Organisations and Careers Representative shall include those listed below.
\begin{enumerate}
	\item Advancing the interests of the JCR to organisations to which the JCR is affiliated under S.O. 9, in association with the President.     
	\item Reporting the results of these organisations' meetings to the General Meeting as requested.
	\item Once a year, hosting a `Careers Day' Event at Merton, with support from the President and/or the Academic Affairs representative.
	\item Maintaining relations with the Merton Society and, when invited, attending meetings.
	\item Supporting the Subject Society Presidents to organise alumni talks
	\item Liaising with the Development Office on the behalf of the JCR, alongside the President.
	\item Advising the JCR and the JCR Committee on issues relating to the Merton Society, Affiliated Organisations or organisations proposed for affiliation.
	\item Maintaining files of correspondence from Affiliated Organisations and the Merton Society.
	\item Publicising the availability of resources and information concerning, and provided by, Affiliated Organisations or the Merton Society.
	\item Assisting the Information and Returning Officer in elections relevant to Affiliated Organisations if JCR assistance is required.
	\item Emailing the JCR three days before an Affiliated Organisation's or the Merton Society's legislative meeting or, failing that, as soon as the agenda is available, with the agenda for the meeting and a brief, objective summary of the motions to be debated.
	\item Updating the JCR Website, no later than 48 hours after the meeting has concluded, giving details of how the JCR's representatives voted at the meeting on each motion, and detailing any other noteworthy matters arising from the meeting.
\end{enumerate}
\section{Arts and Culture Representative}
\npara The Arts Representative shall be responsible for promoting and advancing artistic and cultural activities and endeavour within the JCR.
\npara In each Academic Year, the Scheduled Election of the Arts Representative shall take place in the first OGM of Hilary.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Arts Representative shall include those listed below.
\begin{enumerate}
	\item Being the first point of contact for all matters relating to arts and culture and promoting the flourishing of artistic and cultural endeavour within the JCR.
	\item Ensuring the appointment of a president of the Merton College drama group, The Merton Floats, and monitoring the financial stability of the society.    
	\item Ensuring the appointment of a president of the Merton College Fine Art Society, and monitoring the financial stability of the society.
	\item Ensuring the appointment of a president of the Merton College Music Society, and monitoring the financial stability of the society.
	\item Having responsibility for the JCR Arts Budget.
	\item Ensuring that theatrical productions are staged within College on a regular basis.
	\item Assisting the Merton Floats president in appointing a producer and director, who may not be the same person, for each production to take place under the aegis of that society within College.     
	\item Offering practical help and advice to drama cuppers teams as required.
	\item Maintaining a supply of artists' materials for painting and drawing in the JCR store for the use of the Merton College Fine Art Society.
	\item Coordinating Merton Arts Fest and arranging appropriate events throughout a single week of Trinity Term.
	\item Arranging Mertonbury music festival to take place on Sundial Lawn on the Saturday of Arts Fest Week.
	\item Representing the JCR in attending all meetings of the College Sub-Committee for Pictures, Historic Chattels and Works of Art. 
	\item Arranging opportunities for members of the JCR to display their works of art around College, including liaising with the College Pictures Committee to arrange regular exhibitions of student work in the Savile Room.
	\item Liaising with the Merton College Music Society, Kodaly Choir and Fidelio Orchestra to publicise events, and arrange venues for regular concerts.
\end{enumerate}
\section{Charities Representative}
\npara The Charities Representative shall be responsible for organising and promoting fundraising activities for charitable causes within the JCR and the College.
\npara In each Academic Year, the Scheduled Election for the Charities Representative shall be in the fourth OGM of Michaelmas.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Charities Representative shall include those listed below.
\begin{enumerate}
	\item The organisation of the yearly charities ballot in accordance with Appendix \ref{app:charities_ballot} to decide the two charities that the Junior Members will support for that year, besides the two permanent Junior Members' charities.
	\item The co-ordination and execution of charitable appeals and events within College.
	\item Liaising with the University RAG society through the relevant RAG officer and attending relevant meetings of affiliated organisations.
	\item Convening and co-chairing a meeting of the Junior Members Charities Committee at least once a term (Appendix D).
	\item Publicising the Junior Members Charities Sponsorship Fund.
	\item Promotion and development of the JCR's links with the two permanent Junior Members' charities, The Icolyn Smith Foundation and the Wolvercote Young People's Trust, as well as the two charities chosen yearly.     
	\item Sending regular emails to the JCR with information about charitable events and opportunities, gathered from University and College wide sources.
	\item Organising the termly Charity Formal and liaising with the College kitchen staff to do so.
	\item Maintaining the JCR Food Bank in the Pidge Room and publicising it in emails to the JCR.
\end{enumerate}
\section{Disabled Students' Representative}
\npara The Disabled Students' Representative shall be responsible for representing and advancing the interests of Undergraduates with mental, physical and other health issues or disabilities within the JCR, the College and the University. 
\npara In each Academic Year, the Scheduled Election for the Disabled Students' Representative shall be in the first OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Disabled Students' Representative shall include those listed below.
\begin{enumerate}
	\item Working to improve accessibility on college property.
	\item Acting to prevent discrimination or prejudice on the grounds of disabilities and acting to address it should it arise.
	\item Signposting and promoting resources available to students with mental and physical health issues across the university.
	\item Working to improve provisions made for students with learning difficulties within and around college.
	\item Managing the JCR events (BOPs, JCR-specific formals, and other events at the discretion of the Disabled Students' Representative and the Executive Committee) pre-booking system for students with disabilities or other accessibility-related issues, (not including non-examination academic commitments or social commitments).
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}).
\end{enumerate}
\section{Environment Representative}
\npara The Environment Representative shall be responsible for promoting awareness of environmental issues in the JCR, the College and the University and advancing the interests of the Ordinary Members in those matters.. 
\npara In each Academic Year, the Scheduled Election for the Environment Representative shall be in the fourth OGM of Michaelmas.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Environment Representative shall include those listed below.
\begin{enumerate}
	\item Promoting and organising environmentally friendly practices within the College, including ethical buying and supporting local businesses.
	\item Encouraging and advising students to make individual decisions to lessen their environmental impact.
	\item Encouraging and advising the College to make environmentally conscious changes.
	\item Advising the JCR and JCR Committee on environmental issues.
	\item Representing the JCR on external committees convened by Affiliated Organisations for the consideration and advancement of environmental issues.
	\item Overseeing, in conjunction with the MCR Environment rep, the Merton Bank sale in Freshers' Week. This involves collecting unwanted materials (specified in handover materials), storing them over the long vacation, the sale itself and keeping the storage room tidy.
	\item Moderating the online Facebook trading page `Merton Swap' and advertising it to members of the College.
\end{enumerate}
\section{Ethnic Minority Students' Representative}
\npara The Ethnic Minority Students' Representative shall be responsible for representing and advancing the interests of ethnic minority students within the JCR, the College and the University. 
\npara In each Academic Year, the Scheduled Election for the Ethnic Minority Representative shall be in the second OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Ethnic Minority Students' Representative shall include those listed below.
\begin{enumerate}
	\item Acting to prevent race-based discrimination or prejudice of any kind and addressing it should it arise.
	\item Promoting awareness about issues of racial equality.
	\item Supporting within College external schemes pertaining to ethnic minority students.
	\item Aiding the Access and Equal Opportunities Representative with the organisation of Open Days with a view to encouraging applications from minority groups students.
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}).
	\item Organising social events to promote links with other colleges.
\end{enumerate}
\section{Food and Bar Representative}
\npara The Food and Bar Representative shall be responsible for working to coordinate all JCR business related to food, drink and any related services provided by the JCR or the College.
\npara In each Academic Year, the Scheduled Election for the Food and Bar Representative shall be in the first OGM of Hilary.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Food and Bar Representative shall include those listed below.
\begin{enumerate}
	\item Liaising between the JCR and the Chef, College kitchen staff, and Bar staff. 
	\item Further improving College food. 
	\item Organising the JCR Christmas Dinners.
	\item Organising and or assisting the Entertainment Representatives with the May Morning Breakfast. 
	\item Organising Halfway Hall with College in mid-Hilary Term.
	\item Organising a termly JCR Black Tie Formal.
	\item Helping to organise the Sports Dinner with the Sports and Recreation Representative and Charity Formals with the Charities Representative.
	\item Organising, publicising and hosting a regular JCR bar quiz, and publicising any MCR bar quizzes to the JCR.
	\item Liaising, in conjunction with the President, with College Authorities on any issues relating to the JCR kitchen. 
	\item Liaising with the Domestic Bursar on the issue of dietary requirements.
	\item Advising other Undergraduates planning special meals on how to liaise with Hall (e.g. subject dinners, special formals, Arts Fest).
	\item Ensuring the upkeep of the JCR kitchen, to include checking, on a weekly basis, the presence and state of all JCR kitchen equipment and washing supplies, but excluding the cleaning of said equipment. 
	\item Maintaining and updating the Food Book, while ensuring any overly offensive material is removed.
	\item Maintaining the Merton JCR Food and Bar Representative's tankard.
	\item Maintaining all JCR facilities in the Bar area and the MacKeith Room.
	\item Maintaining, in liaison with the Treasurer, the relevant music solutions in the College Bar.
\end{enumerate}
\section{Gender Equality Representative}
\npara The Gender Equality Representative shall be responsible for advancing and representing the interests of Undergraduates within the JCR, the College and the University, insofar as these interests arise from, or are related to, the gender of Undergraduates.
\npara In each Academic Year, the Scheduled Election of the Gender Equality Representative shall be in the third OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Gender Equality Representative shall include those listed below.
\begin{enumerate}
	\item Promoting gender equality within the College and the University.     
	\item Promoting awareness of sexual health and sexual consent.     
	\item Acting to prevent gender-based discrimination or prejudice of any kind and addressing it should it arise.     
	\item Assisting the Access and Equal Opportunities Representative with the organisation of Open Days with a view to promoting gender equality among applicants.     
	\item Representing the JCR on external committees convened by Affiliated Organisations for the consideration and advancement of gender equality and reporting back to the JCR on any issues arising.     
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).     
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}).
\end{enumerate}
\section{International Students' Representative}
\npara The International Students' Representative shall be responsible representing and advancing the interests of international Undergraduates within the JCR, the College and the University.
\npara In each Academic Year, the Scheduled Election for the International Students' Representative shall be in the second OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the International Students' Representative shall include those listed below.
\begin{enumerate}
	\item Acting to prevent nationality-based discrimination or prejudice of any kind and addressing it should it arise.
	\item Aiding the Access and Equal Opportunities Representative with the organisation of Open Days with a view to encouraging applications from international students.
	\item Representing the JCR on external committees convened by Affiliated Organisations for the consideration and advancement of issues relating to international students and reporting back to the JCR on any issues arising.
	\item Organising the international parenting scheme, in coordination with the Welfare Officers.
	\item Writing and editing the International Freshers' Guide.
	\item Organising, with the Executive Committee, a programme for international students during the weekend before the official Freshers' Week.
	\item Providing information and support about, and lobbying for better provision of, services relevant to international students, such as finance, funding, vacation residence and storage.
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}).
\end{enumerate}
\section{LGBTQIA+ Representative}
\npara The LGBTQIA+ Representative shall be responsible for representing and advancing the interests of members of the LGBTQIA+ community who are current Undergraduates within the JCR, the College and the University.
\npara In each Academic Year, the Scheduled Election for the LGBTQIA+ Representative shall be in the first OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the LGBTQIA+ Representative shall include those listed below.
\begin{enumerate}
	\item Attending the Peer Support training sessions.
	\item Providing a confidential listening service to Undergraduates.
	\item Promoting awareness about issues of sexual health and sexual consent.
	\item Promoting awareness, understanding and acceptance of queer sexualities and genders.
	\item Supporting within College external schemes pertaining to LGBTQIA+ students.
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}).
	\item Ensuring that, as far as possible, there is a Merton presence at all external committees convened by Affiliated Organisations for the consideration and advancement of LGBTQIA+ issues.
	\item Organisation of social events to promote links with other colleges.
\end{enumerate}
\section{Publications and Social Media Officer}
\npara The Publications and Social Media Officer shall be responsible for working to manage and coordinate all JCR business related to JCR-based publications and its outward image on Social Media. 
\npara Two candidates may opt run jointly for this role and shall be treated as if they were one candidate for the purposes of the election. If they are elected, the role shall be held, jointly, by both. A By-Election shall only be held if no incumbent Members remain.
\npara In each Academic Year, the Scheduled Election for the Publications and Social Media Officer shall be in the final OGM of Hilary.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Publications and Social Media Officer shall include those listed below.
\begin{enumerate}
	\item Responsibility for the writing and distribution of a JCR Publication containing amusing and interesting content for the enjoyment of all JCR members.
	\item Managing and maintaining the Merton JCR JCR TikTok account, producing quality content that puts Merton on the map.
	\item Managing the Walter de Merton Twitter account, providing quality content (including but not limited to live-tweeting hustings) for its followers.
	\item Generally managing and improving the outward image of the JCR across all relevant Social Media platforms.
	\item Collating and passing on photos and any other requested content to the college development office and alumni communications when requested.
	\item Responsibility for writing (or editing and improving the previous year's) Freshers guide over the Trinity vac, working with the President and College to produce a useful, engaging, and preferably entertaining document.
\end{enumerate}
\section{Sports and Recreation Representative}
\npara The Sports and Recreation Representative shall be responsible for promoting and advancing sporting activities and recreation and leisure within the JCR. 
\npara In each Academic Year, the Scheduled Election for the Sports and Recreation Representative shall be in the third OGM of Hilary.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Sports and Recreation Representative shall include those listed below.
\begin{enumerate}
	\item Acting as Junior Treasurer of the Amalgamated Clubs.
	\item Attending the termly meetings of the Amalgamated Clubs.
	\item Representing the interests of the JCR as a whole, and of JCR associations individually, to the Amalgamated Clubs.
	\item Attending meetings of the Sports and Grounds Sub-Committee.
	\item Liaising with the captains of all College sporting associations and representing their interests to the JCR Committee.
	\item Acting as spokesperson for the JCR on all sports-related issues.
	\item Arranging a JCR sports day in Trinity Term in association with the Executive Committee, subject to financial approval.
	\item Liaising with College to organise Sports Dinner, and overseeing the awarding of Haigh Ties at the dinner.
	\item Ensuring there are adequate supplies to use the darts, table tennis and pool facilities.
	\item Proposing a motion in the first OGM of Trinity Term to donate an appropriate amount of money, approved by the JCR, to the annual Blues Sports Fund.
	\item With the MCR Admiral of the Fleet, commission the College Boatman to carry out an annual overwinter inspection of the fleet, and commission any subsequent works and/or repairs.
	\item Attend a `Regulations Working Group' each Hilary Term as convened by the MCR Admiral of the Fleet.
	\item Organise the removal of the punts from the river during 0\textsuperscript{th} week Michaelmas Term.
	\item With the MCR Admiral of the Fleet, upkeep of the punts whilst on the river, including bailing rainwater from the punts as needed.
	\item Publicising the booking procedure for the fleet, and advertising the reguations and protocols for its use.
	\item With the MCR Admiral of the Fleet, organising replacement of lost or damaged equipment year-round.
	\item Acting as a point of contact for all bike-related issues in College.
	\item Wearing the Admiral's hat at all General Meetings, and the safeguarding and maintenance of aforementioned hat.
\end{enumerate}
\section{Suspended Students' Representative}
\npara The Suspended Students' Representative shall be responsible for representing  and advancing the interests of suspended and returning Undergraduates in the JCR, the College and the University.
\npara In each Academic Year, the Scheduled Election for the Suspended Students' Representative shall be in the second OGM of Trinity.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Suspended Students' Representative shall include those listed below.
\begin{enumerate}
	\item Being aware of and provide information when requested on current College policies for suspended students and lobby for changes to these where necessary.
	\item Attending the Peer Support training sessions.
	\item Providing a confidential listening service to Undergraduates.
	\item Liaising with members of College staff such as the Chaplain and Senior Tutor on matters concerning suspended students.
	\item Working and liaising with other parties that may be involved in supporting suspended students, such as SusCam, the Student Advice Service, the Welfare Team within College and the Access and Equal Opportunities and \item Academic Affairs Representatives.
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
\end{enumerate}
\section{Events Photographer}
\npara The Events Photographer shall be responsible for the taking, editing and publication of photographs and other documentary material at JCR events.
\npara In each term, the Scheduled Election for the Events Photographer shall be in the third OGM.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Events Photographer shall include those listed below.
\begin{enumerate}
	\item Taking photographs at JCR entertainment events of those present, including all pre-BOP events and other one-off events organized by the Entertainment Representatives.
	\item Liaising with the Sports Representative to arrange for photographs to be taken of all Merton sports teams, at least once, over the duration of the year.
	\item Liaising with other student groups in College to take photographs of events that encompass a full range of activities to represent College life.
	\item Liaising with the Vice President to ensure suitable photographs are sent to them to keep the JCR Website up to date.      
	\item Promptly publicising photographs taken in a means accessible to all members of the JCR, including, but not exclusively, sharing the photographs on the Merton College JCR Photography Facebook group.
	\item Maintaining an archive of JCR photographs for future reference and use.
	\item Respecting the requests of any members of the JCR either not to have their photograph taken by the Events Photographer or to veto and remove from publication any photograph that they are in.
	\item Managing and maintaining the Merton JCR Instagram account, including uploading submissions from Ordinary Members.  Operating the account under an opt out procedure while remaining in accordance with point vii.
\end{enumerate}
\section{Subject Presidents} \label{sec:roles_subjpres}
\npara There shall be a Subject President for each of the following subject groups.	
\begin{enumerate}
	\item Biochemistry
	\item Biology
	\item Chemistry
	\item Classics
	\item Economics and Management
	\item English
	\item History
	\item Law
	\item Mathematics \& Computer Science
	\item Medicine
	\item Modern Languages
	\item Music
	\item Philosophy, Politics and Economics
	\item Physics
\end{enumerate}
Ordinary Members who study joint schools shall be deemed to part of every subject group that their degree encompasses.
\subsection{Role of Subject Presidents}
Each Subject President shall support the Academic Affairs Representative as the representative of all Ordinary Members in that subject group. They shall protect and further the academic interests of all Ordinary Members and endeavour to foster and maintain a vibrant and active community within their subject.
\subsection{Duty to Conduct `Qualifying Elections'} \label{ssec:roles_subjpres_electionduty}
In addition to the duties enumerated in SO \ref{ssec:roles_subjpres_duties}, the Subject President must organise, or ensure the organisation of, a qualifying election for their subject group in accordance with SOs \ref{ssec:roles_subjpres_electionreq}, \ref{ssec:roles_subjpres_replace} and \ref{ssec:roles_subjpres_electionmisc} in any term where no such election has occurred in that term nor in the previous two terms.
\subsection{`Qualifying Elections': Requirements} \label{ssec:roles_subjpres_electionreq}
An election shall be deemed to be qualifying for a given subject group if the Academic Affairs Representative is satisfied that the following conditions are met:

\begin{enumerate}
    \item It is made clear to voters that the winner of the election shall be become Subject President if eligible and willing;
    \item All Ordinary Members in the subject group are able to vote and stand in the election, without being obliged to incur any expense or unreasonable inconvenience;
    \item All persons eligible to vote or stand in the election are members of the relevant subject group, Ordinary Member or otherwise;
    \item Any winner of the election is eligible and willing to become Subject President of the subject group; and
    \item The occurrence and results of the election are reported to the Academic Affairs Representative promptly after it is held.
\end{enumerate}
\subsection{Replacement of Subject Presidents} \label{ssec:roles_subjpres_replace}
A Subject President may leave office by giving written notice to the Academic Affairs Representative. When a Subject President leaves office, the Academic Affairs Representative shall appoint a replacement according to the following procedures:

\begin{enumerate}
    \item If the outgoing Subject President of a given subject group has organised one and only one `qualifying election' pursuant to the requirements of SOs \ref{ssec:roles_subjpres_electionduty} and \ref{ssec:roles_subjpres_electionreq} since their most recent appointment, and this election has produced a winner, the Academic Affairs Representative shall appoint the winner of this election to the Subject Presidency of that subject group.
    \item If the outgoing Subject President fails to nominate a `qualifying election', and a qualifying election which produces a winner is reported to the Academic Affairs Representative within a period of 7 days of full term beginning on and including the day on which the Subject President leaves office, the Academic Affairs Representative shall immediately appoint the winner of this election to the Subject Presidency of that subject group.
    \item If the period of 7 days in SO \ref{ssec:roles_subjpres_replace}.ii passes with no such `qualifying election' being reported to the Academic Affairs Representative, the Academic Affairs Representative shall appoint to that Subject Presidency a willing Ordinary Member in that subject group having due regard to the views and opinions of the Ordinary Members in that subject group.
    \item The candidate with a majority of ballots in accordance with the procedures of each subject group will be deemed to have won.
    \item A RON victory or a tie in the election shall result in the re-opening of nominations. A further `qualifying election' must be held within 7 days.
    \item In the event of a RON victory or a tie in the subsequent `qualifying election', the Academic Affairs Representative shall undertake consultations with the Ordinary Members of the subject group and the Subject President to appoint an incoming Subject President in accordance with the procedures established in SO \ref{ssec:roles_subjpres_replace}.iii.
    \item Subject Presidents shall be appointed for a period in office terminating at the conclusion of Full Term of the third term following the term in which they were appointed.
\end{enumerate}
\subsection{Election of Subject Presidents: Miscellaneous Provisions} \label{ssec:roles_subjpres_electionmisc}
\begin{enumerate}
    \item The conducting of elections shall remain the competence of each subject group. If assistance is required, the Academic Affairs Representative will work with Subject Presidents to assist with the implementation of the electoral procedure.
    \item The Academic Affairs Representative shall act as Returning Officer. To that end, each Subject President must submit to the Academic Affairs Representative the list of candidates running for election prior to the commencement of the election and, within 24 hours of the conclusion of an election, the result, including vote breakdowns for each candidate.
    \item For the avoidance of doubt, no Subject President may serve for a term of office longer than three consecutive University terms. This subsection has retroactive effect.
    \item This does not prevent an Ordinary Member from being reappointed for a second term of office.
    \item All other subject group procedures for the conducting of elections remain operational insofar as they are not superseded by the contents of SOs \ref{ssec:roles_subjpres_electionduty}, \ref{ssec:roles_subjpres_electionreq}, \ref{ssec:roles_subjpres_replace} or \ref{ssec:roles_subjpres_electionmisc}.
\end{enumerate}
\subsection{Duties of Subject Presidents} \label{ssec:roles_subjpres_duties}
In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of each Subject President shall include those listed below.
\begin{enumerate}
    \item Liaising between Ordinary Members and Tutors.
    \item Seeking to ensure appropriate representation of Ordinary Members on the relevant Joint Consultative Committee (JCC) and promoting awareness of the JCC's work.
    \item As a more senior student, being willing to advise informally other students in their subject on matters relating to teaching provision within that subject and, where appropriate, raising issues with the Academic Affairs Representative. This should have the aim of supporting, but not replacing, the existing college parenting, welfare, and academic affairs systems.
    \item Organising or supporting the organisation of at least one subject-based academic event per year, including but not limited to, talks from academics, panel discussions, seminars, workshops, working tables, or visits to local establishments of relevance to the subject.
    \item Organising or supporting the organisation of social events, such as Trinity Term garden parties.
    \item Ensuring the organisation of an annual subject dinner.
    \item Where appropriate, inviting graduate students, tutors, and where cleared with College, alumni within the subject to events, including the annual subject dinner.
    \item Organising the Freshers' Week events, such as subject teas, subject study skills sessions, subject tours, and library inductions, liaising with the Executive Committee, in particular, the Academic Affairs Representative, and library team where appropriate.
    \item Sending an email to all the incoming First-Years in their subject group informing them of their role as Subject President in the above capacities, by Sunday of 0th Week of Michaelmas Term.
    \item Holding at least one meeting per year in which to acquire feedback from Ordinary Members. This feedback should be gathered into a short report and then presented to the Academic Affairs Representative.
    \item Administering and spending the funds from MIFSS allocated to their subject, in accordance with regulations emanating from the Bursary and the Academic Affairs Representative.
\end{enumerate}
\subsection{Funding of Subject Societies: Operation of System} \label{ssec:roles_subjpres_funding}
\begin{enumerate}
    \item There shall be a system for the provision of funds from College to Subject Societies, hereafter referred to as the `Merton Initiative for the Funding of Subject Societies' (MIFSS). The first system shall operate from Hilary Term 2023 to Trinity Term 2023 inclusive, and thereafter, operate on an annual basis from Michaelmas Term to Trinity Term inclusive.
    \item The funding for each subject society (on an annual basis) shall be allocated in proportion to the number of each society. Those in joint schools will have their share split between their societies, except where students in joint schools prefer that their share is allocated to one society. In this case, the Academic Affairs Representative may use their discretion in determining the allocation of the share in conversation with the relevant students in joint schools.
\end{enumerate}
\subsection{Funding of Subject Societies: Guidance on Allocation of Funds} \label{ssec:roles_subjpres_fundingguidance}
\begin{enumerate}
    \item The Subject President may only spend the funds allocated in accordance with regulations issued from time to time by the Bursary or the Academic Affairs Representative.
    \item The Academic Affairs Representative shall ensure that the Subject Presidents are informed of any such regulations.
\end{enumerate}
\subsection{Definitions and Interpretations}
\begin{enumerate}
    \item Unless otherwise stated within SO \ref{sec:roles_subjpres}, any references to `Subject President' in the singular shall be taken to import the plural in the case of a co-presidency system.
    \item For the avoidance of doubt, funds under the MIFSS system are to be construed as `college funds'.
    \item Unless otherwise stated, the terms in SO \ref{sec:roles_subjpres} are to be construed as detailed below. These definitions supersede any definitions to the contrary contained elsewhere within the Standing Orders.
\end{enumerate}
`Ordinary Members' – for the avoidance of doubt, Ordinary Members includes only Undergraduate students.

`Qualifying election' – a `qualifying election' is an election conducted pursuant to the requirements of SOs \ref{ssec:roles_subjpres_electionduty} and \ref{ssec:roles_subjpres_electionreq}.

`Subject President' – unless any contrary intention appears, any references to the singular shall be construed as importing the plural too.

`Subject group' – for the avoidance of doubt, the subject groups are enumerated as follows, notwithstanding any other names they may be known by: Biochemistry; Biology; Chemistry; Classics; Economics and Management; English; History; Law; Mathematics and Computer Science; Medicine; Modern Languages; Music; Philosophy, Politics and Economics; Physics; and for the purposes of §\ref{sec:roles_subjpres} does not include any other societies affiliated, formally or otherwise, to the Subject Societies, including, but not limited to, the Merton College Music Society (MCMS) and the Merton College Poetry Society.

`Subject study skills session' refers to sessions introduced in Michaelmas Term 2018, to be hosted by the Subject President before the end of Week 2 of Michaelmas Term each year, for the giving of subject-specific feedback to first-year undergraduates, with regards to approaching the subject, effective methods of working, and for the answering of any questions.
\section{Information Technology Officer}
\npara The Information Technology Officer shall be responsible for advancing and representing the interests of Undergraduates within the JCR, insofar as these interests arise from, or are related to, Information Technology
\npara In each Academic Year, the Scheduled Election of the Information Technology Officer shall be in the fourth OGM of Hilary.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Information Technology Officer shall include those listed below.
\begin{enumerate}
    \item Liaising with the relevant College Officers concerning the provision of IT facilities and the College Intranet. 
    \item Updating and improving the JCR Website.
    \item Attending the Information Technology Committee 
    \item Maintaining an up-to-date copy of the Standing Orders on the Website in association with the President, on behalf of the Executive Committee. 
    \item Maintaining the server side of the JCR Website. 
    \item Supporting the JCR Committee with use of the JCR Website and other JCR IT, and offering inductions to all new members of the JCR Committee.
\end{enumerate}
\section{Social Backgrounds Representative}
\npara	The Social Backgrounds Representative shall have overall responsibility within the JCR to represent working class, low income, state comprehensive school-educated, and first-generation students, as well as care leavers and estranged students.

\npara In each Academic Year, the Scheduled Election for the Social Backgrounds Representative shall be in the first OGM of Trinity.

\npara	In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Social Backgrounds Representative shall include those listed below. 
\begin{enumerate}
    \item Promoting the welfare of working class, low income, state comprehensive school-educated, first generation, estranged and care leaver students at the college.
    \item Lobbying the college to better support these students, both financially and pastorally.
    \item Ensuring that both college and university resources and services that could be useful to them are well publicised and accessible to them.
    \item Assisting the Access \& Equal Opportunities Representative with the organisation of Open Days with a view to promoting equality between people of different socioeconomic backgrounds among applicants
    \item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee})
    \item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee})
    \item Liaising with Oxford SU’s Class Act campaign in order to keep up to date with and advertise the campaign’s work as well as receive support and advice for the Officer’s work in college.
    \item Working with other representatives within the Equality Sub-Committee in order to work towards common goals and collaborative initiatives in recognition of intersectional issues.
    \item Assisting the Access \& Equal Opportunities Representative with the organisation and maintenance of a JCR community of students in receipt of grants, bursaries or other financial assistance.
\end{enumerate}

\section{Welfare Helpers}
\npara There will be two Welfare Helpers responsible for supporting and working with the two Welfare Reps in their tasks of a non-sensitive nature within the JCR, College, or the University.

\npara The Welfare Helpers shall be elected to Office for the duration of one term. The Scheduled Election shall take place in the last OGM of every term. An individual may hold the role for multiple terms, but must be re-elected.

\npara Welfare Helpers would not have access to data-sensitive information which is temporarily stored by the Welfare Officers.
\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the two Welfare Helpers shall include those listed below: 
\begin{enumerate}
    \item Aiding the Welfare Officers in non-sensitive elements of their roles (including but not necessitating BOPs, Welfare tea, and Freshers’ week) 
    \item Conferring Ordinary members of the JCR to the Welfare Officers when required
    \item Signposting and promoting resources available to students with mental and physical health issues across the university.
    \item Management of any welfare social media accounts jointly with the Welfare Officers
    \item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}).
\end{enumerate}

\section{Transgender Representative}
\npara The Transgender Representative shall be responsible for representing and advancing the interests of current genderqueer Undergraduates within the JCR, the College and the University.

\npara In each Academic Year, the Scheduled Election for the Transgender Representative shall be in the first OGM of Trinity.

\npara In addition to any other responsibilities provided for by the Constitution and Standing Orders, the responsibilities of the Transgender Representative shall include those listed below:
\begin{enumerate}
	\item Attending the Peer Support training sessions.
	\item Providing a confidential listening service to Undergraduates.
	\item Promoting awareness about issues of sexual health and sexual consent. 
	\item Promoting awareness, understanding and acceptance of queer genders. 
	\item Supporting within College external schemes pertaining to transgender students. 
	\item Attending meetings of the Welfare Sub-Committee (S.O.~\ref{ssec:welfare-committee}). 
	\item Attending meetings of the Equality Sub-Committee (S.O.~\ref{ssec:equality-committee}). 
	\item Ensuring that, as far as possible, there is a Merton presence at all external committees convened by Affiliated Organisations for the consideration and advancement of transgender inclusion. 
	\item Organisation of social events to promote links with other colleges.
\end{enumerate}



